Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution

### 2018-01-11 main.tex
Update on Overleaf.

\title{REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case}
%Unstable Star Formation for the Lowest Mass Dwarf Galaxies
\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Greg Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
\author{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

@@

\begin{abstract}
\textbf{Saving this for after the first iteration}
\end{abstract}

@@

\section{Introduction}

Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade. Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc. \citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses. On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM. This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}. See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.

These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution. In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense. In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships. For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.

Due to its complexity, the detailed interstellar medium (ISM) and chemical abundance properties, beyond total metallicity, are sensitive tests of the underlying physical processes that govern galaxy evolution. Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models. There is a considerable body of work examining the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}. These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017} and more detailed quantities such as metallicity distribution functions (MDFs) and abundance evolution of individual species \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} . However, there is a general lack of numerical diversity in these works, as a majority are implemented in some flavor of smoothed particle hydrodynamics (SPH) schemes. Given the known differences between hydrodynamics implementations \citep{Agertz2007,AGORA,AGORA2}, extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}. Additionally, grid-based schemes are able to generally avoid issues with metal mixing, one of the largest model uncertainties in standard SPH codes.

The native SPH scheme is incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017} which, while sophisticated, must still generally be fine-tuned. Even more, a given parameterization is not necessarily applicable generally \citep{Revaz2016}, though recent studies have shown great improvements to this end \citep{Escala2017}. Metal mixing efficiencies may also vary species-by-species (refs), as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}. In part, this is because mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) 
%mm in which they are injected to
    that injects metals into 
the ISM. The variations in how one handles sub-grid metal injection and metal mixing schemes can lead to challenges in connecting models back to the fundamental physics that drives galactic evolution. We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mesh refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies.

Although increasing physical resolution reduces 
%mm one's 
reliance on sub-grid physics, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations \citep[SSPs; as studied in detail in ][]{Revaz2016} do not make physical sense. Below 10$^4$ M$_{\odot}$, SSPs begin to no longer fully sample the IMF, and can no longer be considered average representations of stellar populations; this becomes conceptually problematic at SSP masses comparable to or below the mass of the most massive star ($\sim 100$ M$_{\odot}$). Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Rosdahl2015,Kroupa2013}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}. 
%mm Perhaps the most naive, 
   The most straightforward
solution, though untenable for large scale simulations, is to remove the SSP formalism entirely and simply track stars as individual particles. In this work, we 
%mm follow stars as individual star particles, allowing us to place unprecedented detail on our
     do this, allowing unprecedented detail in our
 accounting of stellar feedback processes and chemical enrichment.

The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution. For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies. \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies. Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.

@@

This paper is the first in a series of papers examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. In this paper we introduce a new method of modeling for feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}. For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer. In addition, we couple to a self-consistent set of stellar yields 
%mm tables from the
to track stellar yields from massive star stellar winds, AGB star winds, and supernovae. We describe each mode of our multi-channel feedback 
%mm implementation 
in detail below, and briefly discuss their implementation in an isolated dwarf galaxy simulation.

@@

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and O column density projections (fourth row), at four different times in the simulation \textit{(list times here)}. In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points. Towards the end of the simulation time, the half light radius is $389 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{ \textbf{need to adjust overlapping labels} Edge-on views of our dwarf galaxy at four different times in its evolution, separated by 100~Myr, beginning with the time at first star formation and ending at 300 Myr. Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and O column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single black dot.  \textbf{use H2 in bottom panel instead}}
\label{fig:panel_x}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on projections/slices. \textbf{use H2 in bottom panel instead}}
\label{fig:panel_z}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.975\linewidth]{scale_height}
\caption{The 30~Myr time average gas disk scale height as a function of radius at various times throughout the simulation.}
\label{fig:scale_height}
\end{figure}

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about \textbf{$6 \times 10^5$ M$_{\odot}$, or roughly 17\%} of the total mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction doubles over time to roughly 35\%. This is because the total amount of mass in the disk decreases through feedback driven winds, but the H$_2$ is preferentially retained. Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}. \textbf{Is it worth also plotting the non-luminous stellar masses here? The total mass in WD's and other SN remnants? This mass is roughly half of the mass of luminous stars at the end of the simulation.}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{phase_diagram.png}
\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation, averaged over the final 50 Myr of simulation time, and showing the whole simulation domain.}
\label{fig:phase}
\end{figure}

@@

The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}. This is particularly not surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve. In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time. The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}). The contribution from the metagalactic background falls below the lower vertical axis limit on this plot. Interestingly, the averaged profile appears nearly flat for most of the disk, with an increase at higher radii due to more recently formed stars. However, the ISRF varies significantly over time, fluctuating by an order of magnitude or more at any given radius. \textbf{Note to remember to discuss: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e. how does this compare to a uniform or 1D radial profile). G$_{eff}$ is convolved with local density and temperature variations, and is thus a bit harder to parse / interpret. Though possibly I should show both?}

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in our galaxy in three different bands, time-averaged over the final 50 Myr of simulation time. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the \ion{H}{1} and \ion{He}{1} ionizing stellar radiation flux, showing average and maximum values only. For these fields the minimum value reaches zero at some point during the examined period at all radii.}
\label{fig:ISRF}
\end{figure}

The bottom panel gives the ionizing photon fluxes for \ion{H}{1} and \ion{He}{1} from stellar radiation {\em only}. Since these fields are tracked directly using ray-tracing radiative transfer, the profiles encode information about local attenuation of these photons from dense, neutral gas. This is the main driver of the differences between these fields and $G_{\rm o}$. The ionizing fields vary much more dramatically at all radii, \textbf{need to figure out how to plot these. median / average mean very different things.}

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots of the ISRF in two flux bands, $G_{\rm o}$ and \ion{H}{1} ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within 25 pc of the midplane of our dwarf galaxy. We note the large difference in color scale between the two plots. Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to \ion{H}{1} ionizing radiation, it does not show up in the \ion{H}{1} ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ since we assume it to be optically thin, though do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

These plots are useful to understand the time-varying properties of the ISRF in a spatially averaged sense. However, the local variations for individual regions can be much larger than is illustrated in these profiles. In Figure~\ref{fig:ISRF_2D} we present the full distribution of $G_{\rm o}$ at the end of the simulation time. This more effectively captures the large spikes in local ISRF from young, massive stars. The azimuthally averaged profiles capture the averaged heating and ionizing effects of the ISRF in our galaxy. This helps reduce star formation by increasing the thermal pressure support and equilibrium temperature of the ISM. However, it is the spikes that act as important local feedback to shut off star formation in dense, collapsing regions that satisfy our star formation criteria.
%mm (Emerick et. al. in prep).  [I'd only insert the reference when there is an actual astro-ph number to support it.]

@@

The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}. We use the 10 Myr averaged SFR to compute the mass loading rates. The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time. This quickly declines towards larger radii, however, with \textbf{check this effectively zero outflow past the virial radius}. \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift. Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below their typical values.

@@

\subsection{Metal Evolution} 
\label{sec:chemical evolution}
\textbf{Commented out all previous discussion of species abundance retention differences and stellar abundances to save for a future paper. Instead, here give a panel plot showing the column densities of the metals at various times?}

>>>>

\title{Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution}
%Unstable Star Formation for the Lowest Mass Dwarf Galaxies
\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Greg Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
\author{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

@@

\begin{abstract}
We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement code \textsc{Enzo}. For the first time in galaxy scale simulations, we are capable of capturing detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae. 
%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species \textbf{list here?}. We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium. We present the first application of these methods on a \textbf{XX Myr} simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. Our methods are capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significant metal enriched outflows, leading to a low metal retention fractions consistent with observations. Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions. We end with a discussion on how this work will impact our understanding of galactic chemical evolution on a species-by-species basis, with first results presented in a companion paper \textit{reference here?}.
\end{abstract}

@@

\section{Introduction}
%
% AE removed below.. MM suggested  skipping both pars.
%
%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade. Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc. \citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses. On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM. This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}. See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics. 
%
%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution. In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense. In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships. For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.

Due to its complexity, the detailed interstellar medium (ISM) and chemical abundance properties of galaxies
%beyond total metallicity
are sensitive tests of the underlying physical processes that govern galaxy evolution. Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models. There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}. These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and abundance evolution of individual species \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .

%\textbf{rework here to the end... focus less on numerics}
% However, there is a general lack of numerical diversity in these works, as a majority are implemented in some flavor of smoothed particle hydrodynamics (SPH) schemes. Given the known differences between hydrodynamics implementations \citep{Agertz2007,AGORA,AGORA2}, extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}. % AE (incorrect statement): Additionally, grid-based schemes are able to generally avoid issues with metal mixing, one of the largest model uncertainties in standard SPH codes.

The native smooth particle hydrodynamics (SPH) scheme is incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017a}. Even more, a given parameterization is not necessarily applicable generally \citep{Revaz2016}, though recent studies have shown great improvements to this end \citep{Escala2017}. Metal mixing efficiencies may also vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) 
%mm in which they are injected to
    that inject metals into 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how one handles sub-grid metal injection and metal mixing schemes can lead to challenges in connecting models to observations and the fundamental physics that drives galaxy evolution. \textbf{Still not sure about this sentence - but I do need a way to cite mentioned papers:} Extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.

Although increasing physical resolution reduces 
%mm one's 
reliance on sub-grid physics, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations (SSPs) are no longer valid \citep[as studied in detail in ][]{Revaz2016}. Below 10$^4$ M$_{\odot}$, SSPs do not fully sample the IMF, and cannot be considered average representations of stellar populations. This is acutely problematic at star particle masses comparable to or below the mass of the most massive individual star (or $\sim 100$ M$_{\odot}$). Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}. 
%mm Perhaps the most naive, 
   The most straightforward
solution is to remove the SSP formalism entirely and simply track stars as individual particles. However, the number of particles required to do so make this computationally prohibitive in all but the smallest of galaxies ($M_{*} \lesssim 10^{7} {\rm M_{\odot}})$, let alone in a cosmological simulation.
%In this work, we 
%mm follow stars as individual star particles, allowing us to place unprecedented detail on our
%     do this, allowing unprecedented detail in our
% accounting of stellar feedback processes and chemical enrichment.

We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mesh refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies. The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies. \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies. 
Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback of both massive stars and AGB stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.

@@

This paper is the first in a series of papers examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}. For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer. In addition, we couple to a self-consistent set of stellar yields %mm tables from the
to track yields from massive star stellar winds, AGB star winds, and supernovae. We describe each mode of our multi-channel feedback 
%mm implementation 
in detail below, and briefly discuss their implementation in an isolated dwarf galaxy simulation.

@@

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation \textit{(list times here)}. In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points. Towards the end of the simulation time, the half light radius is \textbf{$389 \pm 21$ pc}, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{ \textbf{need to adjust overlapping labels} Edge-on views of our dwarf galaxy at four different times in its evolution, separated by 100~Myr, beginning with the time at first star formation and ending at 300 Myr. Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single black dot.}
\label{fig:panel_x}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on projections/slices.}
\label{fig:panel_z}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.975\linewidth]{scale_height}
\caption{The total gas scale height at various times throughout the simulation.}
\label{fig:scale_height}
\end{figure}

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about \textbf{$6 \times 10^5$ M$_{\odot}$, or roughly 17\%} of the total mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction doubles over time to roughly 35\%. This is because the total amount of mass in the disk decreases through feedback driven winds, but the H$_2$ is preferentially retained. Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{phase_diagram.png}
\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gass interior to 0.25~$R_{\rm vir}$, averaged over the final 50 Myr of simulation time. The two red dashed lines show lines of constant pressure for guidance. The region in the lower right corner indicates our density and temperature thresholds for star formation.}
\label{fig:phase}
\end{figure}

@@

The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}. This is particularly not surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve. In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time. The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}). The contribution from the metagalactic background falls below the lower vertical axis limit on this plot. Interestingly, the averaged profile appears nearly flat for most of the disk, with an increase at higher radii due to more recently formed stars. However, the ISRF varies significantly over time, fluctuating by an order of magnitude or more at any given radius.

\textbf{Note to remember to discuss: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e. how does this compare to a uniform or 1D radial profile). G$_{eff}$ is convolved with local density and temperature variations, and is thus a bit harder to parse / interpret. Though possibly I should show both?}

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over the final 50 Myr of simulation time. Here we define the midplace as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the \ion{H}{1} ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values only. \ion{He}{1} is very similar to \ion{H}{1}, with a small vertical offset, and is not shown for clarity.}
\label{fig:ISRF}
\end{figure}

The bottom panel gives the ionizing photon fluxes for \ion{H}{1} from stellar radiation {\em only}. Since this field is tracked directly using ray-tracing radiative transfer, the profile encodes information about local attenuation of these photons from dense, neutral gas. This is the main driver of the differences between this field and $G_{\rm o}$. However, both profiles track each other well as a function of radius. The lack of dramatic trend with radius in both diagrams suggests that one could model the ISRF in low mass dwarf galaxies using a uniform heating / ionization rate; however, this would still fail to capture the fact that any given region of the galaxy will experience order of magnitude or more fluctuations in the incident flux. 
% These fluctuations are likely important in reducing star formation locally around young, massive stars. This effect would be challenging to capture with a simple model. (AE this bit is moved to the end of section)

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 200~Myr of the ISRF in two flux bands, $G_{\rm o}$ and \ion{H}{1} ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to \ion{H}{1} ionizing radiation, it does not show up in the \ion{H}{1} ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ since we assume it to be optically thin, though do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the \ion{H}{1} ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr. This diagram shows how dramatic the increase in ISRF near young, massive stars (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower. The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps). From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy various greatly over time and space in a way that cannot be appropriately captured by an analytic profile. Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation. In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency. It is unclear which of these two modes of feedback is more important in controlling star formation.

%mm (Emerick et. al. in prep).  [I'd only insert the reference when there is an actual astro-ph number to support it.]

@@

The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}. We use the 10 Myr averaged SFR to compute the mass loading rates. The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time. This quickly declines towards larger radii, however, with minimal outflow past the virial radius. \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift. Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below their typical values.

@@

\subsection{Metal Evolution} 
\label{sec:chemical evolution}
\textbf{Commented out all previous discussion of species abundance retention differences and stellar abundances to save for a future paper.}
